```{r}
setwd("~/working_paper/rbci/")
getwd()
```

```{r packages, echo=FALSE, }
library(haven)
library(dplyr)
select <- dplyr::select
library(magrittr)
library(stringr)
library(geosphere)
library(purrr)
library(kableExtra)
library(tidyr)
library(readxl)
library(sf)
library(exactextractr)
library(raster)
library(rgdal)
library(ncdf4)
```

#Afrobarometer & capital cities

```{r}
afro_stack <- readRDS("data/data_rds/afro_stack.rds")
glimpse(afro_stack)

cities <- read_excel("data/data_raw/cities.xlsx")

cities %<>%
  rename(iso=ISO)

data_final <- left_join(afro_stack, cities, by = "iso")%>%
  select(-cname.y)%>%
  rename(cname=cname.x)
```

#Calculate distances

```{r}
calculate_distances <- function(df) {
  df %>%
    mutate(
      dist_cap = if_all(c(longitude, latitude, caplong, caplat), ~!is.na(.)) %>% 
        {if_else(., distGeo(cbind(longitude, latitude), cbind(caplong, caplat)) / 1000, NA_real_)},
      
      dist_ncap = if_all(c(longitude, latitude, ncaplong, ncaplat), ~!is.na(.)) %>%
        {if_else(., distGeo(cbind(longitude, latitude), cbind(ncaplong, ncaplat)) / 1000, NA_real_)},
      
      dist_sndncap = if_all(c(longitude, latitude, sndncaplong, sndncaplat), ~!is.na(.)) %>%
        {if_else(., distGeo(cbind(longitude, latitude), cbind(sndncaplong, sndncaplat)) / 1000, NA_real_)},
      
      dist_cap_ncap = if_all(c(caplong, caplat, ncaplong, ncaplat), ~!is.na(.)) %>%
        {if_else(., distGeo(cbind(caplong, caplat), cbind(ncaplong, ncaplat)) / 1000, NA_real_)},
      
      dist_cap_sndncap = if_all(c(caplong, caplat, sndncaplong, sndncaplat), ~!is.na(.)) %>%
        {if_else(., distGeo(cbind(caplong, caplat), cbind(sndncaplong, sndncaplat)) / 1000, NA_real_)}
    )
}

calculate_stats <- function(df, dist_cols) {
  for(col in dist_cols) {
    log_col <- paste0(col, "_log")
    df <- df %>%
      mutate(!!log_col := log(!!sym(col)))
    
    df <- df %>%
      group_by(cname) %>%
      mutate(
        !!paste0(col, "_max") := max(!!sym(col), na.rm = TRUE),
        !!paste0(col, "_max95") := quantile(!!sym(col), probs = 0.95, na.rm = TRUE),
        !!paste0(col, "_mean") := mean(!!sym(col), na.rm = TRUE)
      ) %>%
      ungroup()
    
    df <- df %>%
      mutate(
        !!paste0(col, "_max_norm") := !!sym(col) / !!sym(paste0(col, "_max")),
        !!paste0(col, "_max_norm95") := if_else(!!sym(col) <= !!sym(paste0(col, "_max95")), 
                                               !!sym(col) / !!sym(paste0(col, "_max95")), 
                                               NA_real_),
        !!paste0(col, "_mean_norm") := !!sym(col) / !!sym(paste0(col, "_mean"))
      )
    
    df <- df %>%
      mutate(
        !!paste0(col, "_max_all") := max(!!sym(col), na.rm = TRUE),
        !!paste0(col, "_max95_all") := quantile(!!sym(col), probs = 0.95, na.rm = TRUE),
        !!paste0(col, "_mean_all") := mean(!!sym(col), na.rm = TRUE)
      )
    
    for(breaks in c(5, 10)) {
      suffix <- if(breaks == 5) "quint" else "dec"
      
      df <- df %>%
        group_by(iso) %>%
        mutate(
          !!paste0(col, "_", suffix) := ntile(!!sym(col), breaks),
          !!paste0(col, "_", suffix, "_log") := ntile(!!sym(log_col), breaks),
          !!paste0(col, "_", suffix, "_max_norm") := ntile(!!sym(paste0(col, "_max_norm")), breaks),
          !!paste0(col, "_", suffix, "_mean_norm") := ntile(!!sym(paste0(col, "_mean_norm")), breaks)
        ) %>%
        ungroup()
      
      df <- df %>%
        mutate(
          !!paste0(col, "_", suffix, "_all") := ntile(!!sym(col), breaks),
          !!paste0(col, "_", suffix, "_log_all") := ntile(!!sym(log_col), breaks),
          !!paste0(col, "_", suffix, "_max_norm_all") := ntile(!!sym(paste0(col, "_max_norm")), breaks),
          !!paste0(col, "_", suffix, "_mean_norm_all") := ntile(!!sym(paste0(col, "_mean_norm")), breaks)
        )
    }
  }
  return(df)
}

data_final %<>%
  calculate_distances() %>%
  calculate_stats(c("dist_cap", "dist_ncap", "dist_sndncap", "dist_cap_ncap", "dist_cap_sndncap"))

saveRDS(data_final, file="data/data_rds/data_final.rds")
```

#Levels

```{r}
folder_path <- "data/data_raw/gadm"

files <- list.files(folder_path, full.names = TRUE)

levels <- data.frame(file = files) %>%
  mutate(country = str_extract(file, "(?<=_)[A-Z]{3}(?=_\\d)"),
         level = as.integer(str_extract(file, "(?<=_)[0-9]+(?=\\.shp$)"))) %>%
  arrange(country, desc(level)) %>%
  distinct(country, .keep_all = TRUE)

levels %<>%
  group_by(country) %>%
  summarise(levels_nb = first(level))

print(levels, n=40)

cty_adm1 <- levels%>%
  filter(levels_nb>=1)%>%
  pull(country)

cty_adm2 <- levels%>%
  filter(levels_nb>=2)%>%
  pull(country)

cty_adm3 <- levels%>%
  filter(levels_nb>=3)%>%
  pull(country)

cty_adm4 <- levels%>%
  filter(levels_nb>=4)%>%
  pull(country)
```

#Administrative boundaries

```{r}
process_admin_level <- function(data, country_code, admin_level) {
  shp_path <- file.path(folder_path, sprintf("gadm41_%s_%d.shp", country_code, admin_level))
  
  panel_sf <- data %>%
    filter(!is.na(latitude) & !is.na(longitude)) %>%
    filter(iso == country_code) %>%
    select(id_unique, latitude, longitude)
  
  regions <- st_read(shp_path, quiet = TRUE)
  regions_valid <- st_make_valid(regions)
  
  panel_sf <- st_as_sf(panel_sf, 
                       coords = c("longitude", "latitude"), 
                       crs = st_crs(regions_valid))
  
  result <- st_join(panel_sf, regions_valid, join = st_intersects) %>%
    as.data.frame() %>%
    select(id_unique, paste0("NAME_", admin_level))
  
  return(result)
}

data_final_adm <- as.data.frame(data_final)

for(i in 1:nrow(levels)) {
  country <- levels$country[i]
  max_level <- levels$levels_nb[i]
  print(paste("Processing country:", country))

  for(level in 1:max_level) {
    print(paste("  Level:", level))
    result <- process_admin_level(data_final_adm, country, level)
    data_final_adm <- left_join(data_final_adm, result, by = "id_unique")
  }
}

data_final_adm %<>%
  mutate(NAME_1 = coalesce(!!!select(., matches("NAME_1")))) %>%
  mutate(NAME_2 = coalesce(!!!select(., matches("NAME_2")))) %>%
  mutate(NAME_3 = coalesce(!!!select(., matches("NAME_3")))) %>%
  mutate(NAME_4 = coalesce(!!!select(., matches("NAME_4")))) %>%
  select(-matches("NAME_\\d+\\.[xy](\\.?[xy])*$")) %>%
  select(everything(), NAME_1, NAME_2, NAME_3, NAME_4)

rm(list = setdiff(ls(), c("data_final_adm", "select", "levels")))

data_final_adm %>%
 filter(is.na(NAME_1)) %>%
 group_by(iso) %>%
 count() %>%
 arrange(desc(n))%>%
  print(n=40)

saveRDS(data_final_adm, file="data/data_rds/data_final_adm.rds")
```

#Raster function

```{r}
rc <- function(x) {
  ifelse(is.na(x), 0,
         ifelse(x < 1, 0,
                ifelse(x >= 1, 1, NA)))
}
```

#3G

##Round 5 (2012)

###adm1

```{r}
ggg_r5_adm1 <- data.frame()

for (country in cty_adm1) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2012 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2012.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm1(3G raster*population density raster)
    ggg_pop_adm1 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm1 <- ggg_pop_adm1

#mean_adm1 (3G raster)
    ggg_adm1 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm1 <- ggg_adm1
    
#mean_adm1(population density raster)
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1
    
#Share of the region’s population with potential access to 3G
    regions$ggg_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, ggg_pop_adm1 / pop_adm1)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, ggg_pop_adm1, ggg_adm1, ggg_adm1_pot, pop_adm1) %>%
      mutate(round = 5)

    ggg_r5_adm1 <- rbind(ggg_r5_adm1, regions)
}

ggg_r5_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r5_adm1))

saveRDS(ggg_r5_adm1, file="data/data_rds/ggg_r5_adm1.rds")
```

###adm2

```{r}
ggg_r5_adm2 <- data.frame()

for (country in cty_adm2) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2012 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2012.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm2(3G raster*population density raster)
    ggg_pop_adm2 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm2 <- ggg_pop_adm2

#mean_adm2 (3G raster)
    ggg_adm2 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm2 <- ggg_adm2
    
#mean_adm2(population density raster)
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2
    
#Share of the region’s population with potential access to 3G
    regions$ggg_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, ggg_pop_adm2 / pop_adm2)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, ggg_pop_adm2, ggg_adm2, ggg_adm2_pot, pop_adm2) %>%
      mutate(round = 5)

    ggg_r5_adm2 <- rbind(ggg_r5_adm2, regions)
}

ggg_r5_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r5_adm2))

saveRDS(ggg_r5_adm2, file="data/data_rds/ggg_r5_adm2.rds")
```

###adm3

```{r}
ggg_r5_adm3 <- data.frame()

for (country in cty_adm3) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2012 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2012.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm3(3G raster*population density raster)
    ggg_pop_adm3 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm3 <- ggg_pop_adm3

#mean_adm3 (3G raster)
    ggg_adm3 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm3 <- ggg_adm3
    
#mean_adm3(population density raster)
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3
    
#Share of the region’s population with potential access to 3G
    regions$ggg_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, ggg_pop_adm3 / pop_adm3)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, ggg_pop_adm3, ggg_adm3, ggg_adm3_pot, pop_adm3) %>%
      mutate(round = 5)

    ggg_r5_adm3 <- rbind(ggg_r5_adm3, regions)
}

ggg_r5_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r5_adm3))

saveRDS(ggg_r5_adm3, file="data/data_rds/ggg_r5_adm3.rds")
```

###adm_merge

```{r}
ggg_r5_adm1 <- readRDS("data/data_rds/ggg_r5_adm1.rds")
ggg_r5_adm2 <- readRDS("data/data_rds/ggg_r5_adm2.rds")
ggg_r5_adm3 <- readRDS("data/data_rds/ggg_r5_adm3.rds")

ggg_r5 <- merge(ggg_r5_adm1, ggg_r5_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
ggg_r5 <- merge(ggg_r5, ggg_r5_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(ggg_r5, file="data/data_rds/ggg_r5.rds")
```

##Round 6 (2015)

###adm1

```{r}
ggg_r6_adm1 <- data.frame()

for (country in cty_adm1) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2015 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2015.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2015_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm1(3G raster*population density raster)
    ggg_pop_adm1 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm1 <- ggg_pop_adm1

#mean_adm1 (3G raster)
    ggg_adm1 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm1 <- ggg_adm1
    
#mean_adm1(population density raster)
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1
    
#Share of the region’s population with potential access to 3G
    regions$ggg_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, ggg_pop_adm1 / pop_adm1)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, ggg_pop_adm1, ggg_adm1, ggg_adm1_pot, pop_adm1) %>%
      mutate(round = 6)

    ggg_r6_adm1 <- rbind(ggg_r6_adm1, regions)
}

ggg_r6_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r6_adm1))

saveRDS(ggg_r6_adm1, file="data/data_rds/ggg_r6_adm1.rds")
```

###adm2

```{r}
ggg_r6_adm2 <- data.frame()

for (country in cty_adm2) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2015 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2015.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2015_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm2(3G raster*population density raster)
    ggg_pop_adm2 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm2 <- ggg_pop_adm2

#mean_adm2 (3G raster)
    ggg_adm2 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm2 <- ggg_adm2
    
#mean_adm2(population density raster)
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2
    
#Share of the region’s population with potential access to 3G
    regions$ggg_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, ggg_pop_adm2 / pop_adm2)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, ggg_pop_adm2, ggg_adm2, ggg_adm2_pot, pop_adm2) %>%
      mutate(round = 6)

    ggg_r6_adm2 <- rbind(ggg_r6_adm2, regions)
}

ggg_r6_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r6_adm2))

saveRDS(ggg_r6_adm2, file="data/data_rds/ggg_r6_adm2.rds")
```

###adm3

```{r}
ggg_r6_adm3 <- data.frame()

for (country in cty_adm3) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2015 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2015.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2015_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm3(3G raster*population density raster)
    ggg_pop_adm3 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm3 <- ggg_pop_adm3

#mean_adm3 (3G raster)
    ggg_adm3 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm3 <- ggg_adm3
    
#mean_adm3(population density raster)
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3
    
#Share of the region’s population with potential access to 3G
    regions$ggg_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, ggg_pop_adm3 / pop_adm3)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, ggg_pop_adm3, ggg_adm3, ggg_adm3_pot, pop_adm3) %>%
      mutate(round = 6)

    ggg_r6_adm3 <- rbind(ggg_r6_adm3, regions)
}

ggg_r6_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r6_adm3))

saveRDS(ggg_r6_adm3, file="data/data_rds/ggg_r6_adm3.rds")
```

###adm_merge

```{r}
ggg_r6_adm1 <- readRDS("data/data_rds/ggg_r6_adm1.rds")
ggg_r6_adm2 <- readRDS("data/data_rds/ggg_r6_adm2.rds")
ggg_r6_adm3 <- readRDS("data/data_rds/ggg_r6_adm3.rds")

ggg_r6 <- merge(ggg_r6_adm1, ggg_r6_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
ggg_r6 <- merge(ggg_r6, ggg_r6_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(ggg_r6, file="data/data_rds/ggg_r6.rds")
```

##Round 7 (2017)

###adm1

```{r}
ggg_r7_adm1 <- data.frame()

for (country in cty_adm1) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2017 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2017.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2017_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm1(3G raster*population density raster)
    ggg_pop_adm1 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm1 <- ggg_pop_adm1

#mean_adm1 (3G raster)
    ggg_adm1 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm1 <- ggg_adm1
    
#mean_adm1(population density raster)
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1
    
#Share of the region’s population with potential access to 3G
    regions$ggg_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, ggg_pop_adm1 / pop_adm1)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, ggg_pop_adm1, ggg_adm1, ggg_adm1_pot, pop_adm1) %>%
      mutate(round = 7)

    ggg_r7_adm1 <- rbind(ggg_r7_adm1, regions)
}

ggg_r7_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r7_adm1))

saveRDS(ggg_r7_adm1, file="data/data_rds/ggg_r7_adm1.rds")
```

###adm2

```{r}
ggg_r7_adm2 <- data.frame()

for (country in cty_adm2) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2017 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2017.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2017_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm2(3G raster*population density raster)
    ggg_pop_adm2 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm2 <- ggg_pop_adm2

#mean_adm2 (3G raster)
    ggg_adm2 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm2 <- ggg_adm2
    
#mean_adm2(population density raster)
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2
    
#Share of the region’s population with potential access to 3G
    regions$ggg_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, ggg_pop_adm2 / pop_adm2)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, ggg_pop_adm2, ggg_adm2, ggg_adm2_pot, pop_adm2) %>%
      mutate(round = 7)

    ggg_r7_adm2 <- rbind(ggg_r7_adm2, regions)
}

ggg_r7_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r7_adm2))

saveRDS(ggg_r7_adm2, file="data/data_rds/ggg_r7_adm2.rds")
```

###adm3

```{r}
ggg_r7_adm3 <- data.frame()

for (country in cty_adm3) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2017 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2017.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2017_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm3(3G raster*population density raster)
    ggg_pop_adm3 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm3 <- ggg_pop_adm3

#mean_adm3 (3G raster)
    ggg_adm3 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm3 <- ggg_adm3
    
#mean_adm3(population density raster)
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3
    
#Share of the region’s population with potential access to 3G
    regions$ggg_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, ggg_pop_adm3 / pop_adm3)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, ggg_pop_adm3, ggg_adm3, ggg_adm3_pot, pop_adm3) %>%
      mutate(round = 7)

    ggg_r7_adm3 <- rbind(ggg_r7_adm3, regions)
}

ggg_r7_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r7_adm3))

saveRDS(ggg_r7_adm3, file="data/data_rds/ggg_r7_adm3.rds")
```

###adm_merge

```{r}
ggg_r7_adm1 <- readRDS("data/data_rds/ggg_r7_adm1.rds")
ggg_r7_adm2 <- readRDS("data/data_rds/ggg_r7_adm2.rds")
ggg_r7_adm3 <- readRDS("data/data_rds/ggg_r7_adm3.rds")

ggg_r7 <- merge(ggg_r7_adm1, ggg_r7_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
ggg_r7 <- merge(ggg_r7, ggg_r7_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(ggg_r7, file="data/data_rds/ggg_r7.rds")
```

##Round 8 (2020)

###adm1

```{r}
ggg_r8_adm1 <- data.frame()

for (country in cty_adm1) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2020 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2020.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2020_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm1(3G raster*population density raster)
    ggg_pop_adm1 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm1 <- ggg_pop_adm1

#mean_adm1 (3G raster)
    ggg_adm1 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm1 <- ggg_adm1
    
#mean_adm1(population density raster)
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1
    
#Share of the region’s population with potential access to 3G
    regions$ggg_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, ggg_pop_adm1 / pop_adm1)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, ggg_pop_adm1, ggg_adm1, ggg_adm1_pot, pop_adm1) %>%
      mutate(round = 8)

    ggg_r8_adm1 <- rbind(ggg_r8_adm1, regions)
}

ggg_r8_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r8_adm1))

saveRDS(ggg_r8_adm1, file="data/data_rds/ggg_r8_adm1.rds")
```

###adm2

```{r}
ggg_r8_adm2 <- data.frame()

for (country in cty_adm2) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2020 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2020.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2020_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm2(3G raster*population density raster)
    ggg_pop_adm2 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm2 <- ggg_pop_adm2

#mean_adm2 (3G raster)
    ggg_adm2 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm2 <- ggg_adm2
    
#mean_adm2(population density raster)
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2
    
#Share of the region’s population with potential access to 3G
    regions$ggg_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, ggg_pop_adm2 / pop_adm2)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, ggg_pop_adm2, ggg_adm2, ggg_adm2_pot, pop_adm2) %>%
      mutate(round = 8)

    ggg_r8_adm2 <- rbind(ggg_r8_adm2, regions)
}

ggg_r8_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r8_adm2))

saveRDS(ggg_r8_adm2, file="data/data_rds/ggg_r8_adm2.rds")
```

###adm3

```{r}
ggg_r8_adm3 <- data.frame()

for (country in cty_adm3) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2020 - GeoTIFF/Data_MCE/ByCountry/MCE_3G/MCE_", country, "3G_2020.tif")
    ggg <- raster(tiff_file)
    ggg_wgs84 <- projectRaster(ggg, crs = CRS("+proj=longlat +datum=WGS84"))
    ggg_wgs84_recode <- calc(ggg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(ggg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(ggg_wgs84_recode))
    }

    ggg_wgs84_cropped <- crop(ggg_wgs84_recode, extent(country_shp))
    ggg_wgs84_masked <- mask(ggg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2020_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(ggg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, ggg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(ggg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 3G per square kilometer: 3G raster*population density raster
    ggg_pop <- ggg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm3(3G raster*population density raster)
    ggg_pop_adm3 <- exact_extract(ggg_pop, regions, 'mean')
    regions$ggg_pop_adm3 <- ggg_pop_adm3

#mean_adm3 (3G raster)
    ggg_adm3 <- exact_extract(ggg_wgs84_masked, regions, 'mean')
    regions$ggg_adm3 <- ggg_adm3
    
#mean_adm3(population density raster)
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3
    
#Share of the region’s population with potential access to 3G
    regions$ggg_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, ggg_pop_adm3 / pop_adm3)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, ggg_pop_adm3, ggg_adm3, ggg_adm3_pot, pop_adm3) %>%
      mutate(round = 8)

    ggg_r8_adm3 <- rbind(ggg_r8_adm3, regions)
}

ggg_r8_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(ggg_r8_adm3))

saveRDS(ggg_r8_adm3, file="data/data_rds/ggg_r8_adm3.rds")
```

###adm_merge

```{r}
ggg_r8_adm1 <- readRDS("data/data_rds/ggg_r8_adm1.rds")
ggg_r8_adm2 <- readRDS("data/data_rds/ggg_r8_adm2.rds")
ggg_r8_adm3 <- readRDS("data/data_rds/ggg_r8_adm3.rds")

ggg_r8 <- merge(ggg_r8_adm1, ggg_r8_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
ggg_r8 <- merge(ggg_r8, ggg_r8_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(ggg_r8, file="data/data_rds/ggg_r8.rds")
```

## Merge 3G

```{r}
ggg_r5 <- readRDS("data/data_rds/ggg_r5.rds")
ggg_r6 <- readRDS("data/data_rds/ggg_r6.rds")
ggg_r7 <- readRDS("data/data_rds/ggg_r7.rds")
ggg_r8 <- readRDS("data/data_rds/ggg_r8.rds")

ggg_rounds <- list(ggg_r5, ggg_r6, ggg_r7, ggg_r8)

ggg_stack <- bind_rows(ggg_rounds)

saveRDS(ggg_stack, file="data/data_rds/ggg_stack.rds")
```


#2G

##Round 5 (2012)

###adm1

```{r}
gg_r5_adm1 <- data.frame()

for (country in cty_adm1) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2012 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2012.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm1(2G raster*population density raster)
    gg_pop_adm1 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm1 <- gg_pop_adm1

#mean_adm1 (2G raster)
    gg_adm1 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm1 <- gg_adm1
    
#mean_adm1(population density raster)
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1
    
#Share of the region’s population with potential access to 2G
    regions$gg_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, gg_pop_adm1 / pop_adm1)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, gg_pop_adm1, gg_adm1, gg_adm1_pot, pop_adm1) %>%
      mutate(round = 5)

    gg_r5_adm1 <- rbind(gg_r5_adm1, regions)
}

gg_r5_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r5_adm1))

saveRDS(gg_r5_adm1, file="data/data_rds/gg_r5_adm1.rds")
```

###adm2

```{r}
gg_r5_adm2 <- data.frame()

for (country in cty_adm2) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2012 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2012.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm2(2G raster*population density raster)
    gg_pop_adm2 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm2 <- gg_pop_adm2

#mean_adm2 (2G raster)
    gg_adm2 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm2 <- gg_adm2
    
#mean_adm2(population density raster)
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2
    
#Share of the region’s population with potential access to 2G
    regions$gg_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, gg_pop_adm2 / pop_adm2)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, gg_pop_adm2, gg_adm2, gg_adm2_pot, pop_adm2) %>%
      mutate(round = 5)

    gg_r5_adm2 <- rbind(gg_r5_adm2, regions)
}

gg_r5_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r5_adm2))

saveRDS(gg_r5_adm2, file="data/data_rds/gg_r5_adm2.rds")
```

###adm3

```{r}
gg_r5_adm3 <- data.frame()

for (country in cty_adm3) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2012 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2012.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm3(2G raster*population density raster)
    gg_pop_adm3 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm3 <- gg_pop_adm3

#mean_adm3 (2G raster)
    gg_adm3 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm3 <- gg_adm3
    
#mean_adm3(population density raster)
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3
    
#Share of the region’s population with potential access to 2G
    regions$gg_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, gg_pop_adm3 / pop_adm3)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, gg_pop_adm3, gg_adm3, gg_adm3_pot, pop_adm3) %>%
      mutate(round = 5)

    gg_r5_adm3 <- rbind(gg_r5_adm3, regions)
}

gg_r5_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r5_adm3))

saveRDS(gg_r5_adm3, file="data/data_rds/gg_r5_adm3.rds")
```

###adm_merge

```{r}
gg_r5_adm1 <- readRDS("data/data_rds/gg_r5_adm1.rds")
gg_r5_adm2 <- readRDS("data/data_rds/gg_r5_adm2.rds")
gg_r5_adm3 <- readRDS("data/data_rds/gg_r5_adm3.rds")

gg_r5 <- merge(gg_r5_adm1, gg_r5_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
gg_r5 <- merge(gg_r5, gg_r5_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(gg_r5, file="data/data_rds/gg_r5.rds")
```

##Round 6 (2015)

###adm1

```{r}
gg_r6_adm1 <- data.frame()

for (country in cty_adm1) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2015 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2015.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2015_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm1(2G raster*population density raster)
    gg_pop_adm1 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm1 <- gg_pop_adm1

#mean_adm1 (2G raster)
    gg_adm1 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm1 <- gg_adm1
    
#mean_adm1(population density raster)
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1
    
#Share of the region’s population with potential access to 2G
    regions$gg_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, gg_pop_adm1 / pop_adm1)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, gg_pop_adm1, gg_adm1, gg_adm1_pot, pop_adm1) %>%
      mutate(round = 6)

    gg_r6_adm1 <- rbind(gg_r6_adm1, regions)
}

gg_r6_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r6_adm1))

saveRDS(gg_r6_adm1, file="data/data_rds/gg_r6_adm1.rds")
```

###adm2

```{r}
gg_r6_adm2 <- data.frame()

for (country in cty_adm2) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2015 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2015.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2015_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm2(2G raster*population density raster)
    gg_pop_adm2 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm2 <- gg_pop_adm2

#mean_adm2 (2G raster)
    gg_adm2 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm2 <- gg_adm2
    
#mean_adm2(population density raster)
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2
    
#Share of the region’s population with potential access to 2G
    regions$gg_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, gg_pop_adm2 / pop_adm2)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, gg_pop_adm2, gg_adm2, gg_adm2_pot, pop_adm2) %>%
      mutate(round = 6)

    gg_r6_adm2 <- rbind(gg_r6_adm2, regions)
}

gg_r6_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r6_adm2))

saveRDS(gg_r6_adm2, file="data/data_rds/gg_r6_adm2.rds")
```

###adm3

```{r}
gg_r6_adm3 <- data.frame()

for (country in cty_adm3) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2015 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2015.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2015_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm3(2G raster*population density raster)
    gg_pop_adm3 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm3 <- gg_pop_adm3

#mean_adm3 (2G raster)
    gg_adm3 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm3 <- gg_adm3
    
#mean_adm3(population density raster)
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3
    
#Share of the region’s population with potential access to 2G
    regions$gg_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, gg_pop_adm3 / pop_adm3)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, gg_pop_adm3, gg_adm3, gg_adm3_pot, pop_adm3) %>%
      mutate(round = 6)

    gg_r6_adm3 <- rbind(gg_r6_adm3, regions)
}

gg_r6_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r6_adm3))

saveRDS(gg_r6_adm3, file="data/data_rds/gg_r6_adm3.rds")
```

###adm_merge

```{r}
gg_r6_adm1 <- readRDS("data/data_rds/gg_r6_adm1.rds")
gg_r6_adm2 <- readRDS("data/data_rds/gg_r6_adm2.rds")
gg_r6_adm3 <- readRDS("data/data_rds/gg_r6_adm3.rds")

gg_r6 <- merge(gg_r6_adm1, gg_r6_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
gg_r6 <- merge(gg_r6, gg_r6_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(gg_r6, file="data/data_rds/gg_r6.rds")
```

##Round 7 (2017)

###adm1

```{r}
gg_r7_adm1 <- data.frame()

for (country in cty_adm1) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2017 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2017.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2017_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm1(2G raster*population density raster)
    gg_pop_adm1 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm1 <- gg_pop_adm1

#mean_adm1 (2G raster)
    gg_adm1 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm1 <- gg_adm1
    
#mean_adm1(population density raster)
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1
    
#Share of the region’s population with potential access to 2G
    regions$gg_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, gg_pop_adm1 / pop_adm1)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, gg_pop_adm1, gg_adm1, gg_adm1_pot, pop_adm1) %>%
      mutate(round = 7)

    gg_r7_adm1 <- rbind(gg_r7_adm1, regions)
}

gg_r7_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r7_adm1))

saveRDS(gg_r7_adm1, file="data/data_rds/gg_r7_adm1.rds")
```

###adm2

```{r}
gg_r7_adm2 <- data.frame()

for (country in cty_adm2) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2017 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2017.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2017_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm2(2G raster*population density raster)
    gg_pop_adm2 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm2 <- gg_pop_adm2

#mean_adm2 (2G raster)
    gg_adm2 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm2 <- gg_adm2
    
#mean_adm2(population density raster)
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2
    
#Share of the region’s population with potential access to 2G
    regions$gg_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, gg_pop_adm2 / pop_adm2)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, gg_pop_adm2, gg_adm2, gg_adm2_pot, pop_adm2) %>%
      mutate(round = 7)

    gg_r7_adm2 <- rbind(gg_r7_adm2, regions)
}

gg_r7_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r7_adm2))

saveRDS(gg_r7_adm2, file="data/data_rds/gg_r7_adm2.rds")
```

###adm3

```{r}
gg_r7_adm3 <- data.frame()

for (country in cty_adm3) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2017 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2017.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2017_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm3(2G raster*population density raster)
    gg_pop_adm3 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm3 <- gg_pop_adm3

#mean_adm3 (2G raster)
    gg_adm3 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm3 <- gg_adm3
    
#mean_adm3(population density raster)
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3
    
#Share of the region’s population with potential access to 2G
    regions$gg_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, gg_pop_adm3 / pop_adm3)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, gg_pop_adm3, gg_adm3, gg_adm3_pot, pop_adm3) %>%
      mutate(round = 7)

    gg_r7_adm3 <- rbind(gg_r7_adm3, regions)
}

gg_r7_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r7_adm3))

saveRDS(gg_r7_adm3, file="data/data_rds/gg_r7_adm3.rds")
```

###adm_merge

```{r}
gg_r7_adm1 <- readRDS("data/data_rds/gg_r7_adm1.rds")
gg_r7_adm2 <- readRDS("data/data_rds/gg_r7_adm2.rds")
gg_r7_adm3 <- readRDS("data/data_rds/gg_r7_adm3.rds")

gg_r7 <- merge(gg_r7_adm1, gg_r7_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
gg_r7 <- merge(gg_r7, gg_r7_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(gg_r7, file="data/data_rds/gg_r7.rds")
```

##Round 8 (2020)

###adm1

```{r}
gg_r8_adm1 <- data.frame()

for (country in cty_adm1) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2020 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2020.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2020_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm1(2G raster*population density raster)
    gg_pop_adm1 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm1 <- gg_pop_adm1

#mean_adm1 (2G raster)
    gg_adm1 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm1 <- gg_adm1
    
#mean_adm1(population density raster)
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1
    
#Share of the region’s population with potential access to 2G
    regions$gg_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, gg_pop_adm1 / pop_adm1)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, gg_pop_adm1, gg_adm1, gg_adm1_pot, pop_adm1) %>%
      mutate(round = 8)

    gg_r8_adm1 <- rbind(gg_r8_adm1, regions)
}

gg_r8_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r8_adm1))

saveRDS(gg_r8_adm1, file="data/data_rds/gg_r8_adm1.rds")
```

###adm2

```{r}
gg_r8_adm2 <- data.frame()

for (country in cty_adm2) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2020 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2020.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2020_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm2(2G raster*population density raster)
    gg_pop_adm2 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm2 <- gg_pop_adm2

#mean_adm2 (2G raster)
    gg_adm2 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm2 <- gg_adm2
    
#mean_adm2(population density raster)
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2
    
#Share of the region’s population with potential access to 2G
    regions$gg_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, gg_pop_adm2 / pop_adm2)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, gg_pop_adm2, gg_adm2, gg_adm2_pot, pop_adm2) %>%
      mutate(round = 8)

    gg_r8_adm2 <- rbind(gg_r8_adm2, regions)
}

gg_r8_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r8_adm2))

saveRDS(gg_r8_adm2, file="data/data_rds/gg_r8_adm2.rds")
```

###adm3

```{r}
gg_r8_adm3 <- data.frame()

for (country in cty_adm3) {
    tiff_file <- paste0("data/data_raw/collins_recode/Mobile Coverage Explorer v2020 - GeoTIFF/Data_MCE/ByCountry/MCE_2G/MCE_", country, "2G_2020.tif")
    gg <- raster(tiff_file)
    gg_wgs84 <- projectRaster(gg, crs = CRS("+proj=longlat +datum=WGS84"))
    gg_wgs84_recode <- calc(gg_wgs84, fun = rc)

    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(gg_wgs84_recode), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(gg_wgs84_recode))
    }

    gg_wgs84_cropped <- crop(gg_wgs84_recode, extent(country_shp))
    gg_wgs84_masked <- mask(gg_wgs84_cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2020_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    if (!all(res(gg_wgs84_masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, gg_wgs84_masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(gg_wgs84_masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

#Number of people with potential access to 2G per square kilometer: 2G raster*population density raster
    gg_pop <- gg_wgs84_masked * pop_wgs84_resampled
    
#mean_adm3(2G raster*population density raster)
    gg_pop_adm3 <- exact_extract(gg_pop, regions, 'mean')
    regions$gg_pop_adm3 <- gg_pop_adm3

#mean_adm3 (2G raster)
    gg_adm3 <- exact_extract(gg_wgs84_masked, regions, 'mean')
    regions$gg_adm3 <- gg_adm3
    
#mean_adm3(population density raster)
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3
    
#Share of the region’s population with potential access to 2G
    regions$gg_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, gg_pop_adm3 / pop_adm3)

    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, gg_pop_adm3, gg_adm3, gg_adm3_pot, pop_adm3) %>%
      mutate(round = 8)

    gg_r8_adm3 <- rbind(gg_r8_adm3, regions)
}

gg_r8_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(gg_r8_adm3))

saveRDS(gg_r8_adm3, file="data/data_rds/gg_r8_adm3.rds")
```

###adm_merge

```{r}
gg_r8_adm1 <- readRDS("data/data_rds/gg_r8_adm1.rds")
gg_r8_adm2 <- readRDS("data/data_rds/gg_r8_adm2.rds")
gg_r8_adm3 <- readRDS("data/data_rds/gg_r8_adm3.rds")

gg_r8 <- merge(gg_r8_adm1, gg_r8_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
gg_r8 <- merge(gg_r8, gg_r8_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(gg_r8, file="data/data_rds/gg_r8.rds")
```

## Merge 2G

```{r}
gg_r5 <- readRDS("data/data_rds/gg_r5.rds")
gg_r6 <- readRDS("data/data_rds/gg_r6.rds")
gg_r7 <- readRDS("data/data_rds/gg_r7.rds")
gg_r8 <- readRDS("data/data_rds/gg_r8.rds")

gg_rounds <- list(gg_r5, gg_r6, gg_r7, gg_r8)

gg_stack <- bind_rows(gg_rounds)

saveRDS(gg_stack, file="data/data_rds/gg_stack.rds")
```

# Merge Internet

```{r}
# -----------------------------------------------------------------------------
# MERGING AND PROCESSING REGIONAL INTERNET DATA
# -----------------------------------------------------------------------------

# -----------------------------------------------------------------------------
# 1. LOAD DATA
# -----------------------------------------------------------------------------
gg_stack <- readRDS("data/data_rds/gg_stack.rds")
ggg_stack <- readRDS("data/data_rds/ggg_stack.rds")

# -----------------------------------------------------------------------------
# 2. MERGE DATASETS
# -----------------------------------------------------------------------------
# Merge gg_stack with ggg_stack by region identifiers and round
int_stack <- gg_stack %>%
  left_join(ggg_stack, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))

# Save intermediate merged internet dataset
saveRDS(int_stack, file = "data/data_rds/int_stack.rds")

# -----------------------------------------------------------------------------
# 3. CLEAN MERGED DATA
# -----------------------------------------------------------------------------
# Coalesce population variables from both datasets (take first non-NA value)
int_stack %<>%
  mutate(
    pop_adm1 = coalesce(pop_adm1.x, pop_adm1.y),
    pop_adm2 = coalesce(pop_adm2.x, pop_adm2.y),
    pop_adm3 = coalesce(pop_adm3.x, pop_adm3.y)
  )

# Remove duplicate columns ending with .x and .y
int_stack %<>%
  select(-ends_with(".x"), -ends_with(".y"))

# -----------------------------------------------------------------------------
# 4. MERGE WITH FINAL DATASET
# -----------------------------------------------------------------------------
# Load data_final dataset
data_final <- readRDS("data/data_rds/data_final.rds")

# Merge final dataset with internet stack
data_final %<>%
  left_join(int_stack, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))

# -----------------------------------------------------------------------------
# 5. REGION CLASSIFICATION
# -----------------------------------------------------------------------------
# Define country groups by administrative level
countries_adm1 <- c("GHA", "KEN", "MOZ", "MWI", "NGA", "TZA", "UGA", "ZMB", "ZWE")
countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")

# -----------------------------------------------------------------------------
# 6. CREATE REGION POTENTIAL VARIABLES
# -----------------------------------------------------------------------------
# Generate region-specific variables based on country classification
data_final %<>%
  # Create gg region potential by admin level
  mutate(gg_region_pot = case_when(
    iso %in% countries_adm1 ~ gg_adm1_pot,
    iso %in% countries_adm2 ~ gg_adm2_pot,
    TRUE ~ NA_integer_
  )) %>%
  # Create ggg region potential by admin level
  mutate(ggg_region_pot = case_when(
    iso %in% countries_adm1 ~ ggg_adm1_pot,
    iso %in% countries_adm2 ~ ggg_adm2_pot,
    TRUE ~ NA_integer_
  )) %>%
  # Create combined coverage variable, prioritizing 3G data
  mutate(cvg_region_pot = ifelse(is.na(ggg_region_pot), gg_region_pot, ggg_region_pot))

# -----------------------------------------------------------------------------
# 7. POPULATION VARIABLES
# -----------------------------------------------------------------------------
# Create region-specific population density variables
data_final %<>%
  mutate(pop_region = case_when(
    iso %in% countries_adm1 ~ pop_adm1,
    iso %in% countries_adm2 ~ pop_adm2,
    TRUE ~ NA_integer_
  )) %>%
  mutate(pop_region_log = log(pop_region + 1))

# -----------------------------------------------------------------------------
# 8. CREATE REGION AND TIME IDENTIFIERS
# -----------------------------------------------------------------------------
# Generate unique IDs for regions and time periods
data_final %<>%
  # Create unique identifiers for administrative regions
  group_by(NAME_2) %>%
  mutate(name2_id = cur_group_id()) %>%
  ungroup() %>%
  group_by(NAME_1) %>%
  mutate(name1_id = cur_group_id()) %>%
  ungroup() %>%
  
  # Create time-region identifiers for ADM1
  mutate(adm1_time = case_when(
    iso %in% countries_adm1 ~ name1_id * 10000 + round,
    TRUE ~ NA_integer_
  )) %>%
  mutate(adm1_time = as.integer(as.factor(adm1_time))) %>%
  
  # Create time-region identifiers for ADM2
  mutate(adm2_time = case_when(
    iso %in% countries_adm2 ~ name2_id * 10000 + round,
    TRUE ~ NA_integer_
  )) %>%
  mutate(adm2_time = as.integer(as.factor(adm2_time)))

# Create country-round and region-time identifiers
data_final %<>%
  mutate(country_round = as.numeric(paste0(round, ccode))) %>%
  # Create general region-time identifier based on administrative level
  mutate(region_time = case_when(
    iso %in% countries_adm1 ~ name1_id * 10000 + round,
    iso %in% countries_adm2 ~ name2_id * 10000 + round,
    TRUE ~ NA_integer_
  )) %>%
  mutate(region_time = as.integer(as.factor(region_time)))

# -----------------------------------------------------------------------------
# 9. SAVE FINAL DATASETS
# -----------------------------------------------------------------------------
# Save as R and Stata files
saveRDS(data_final, file = "data/data_rds/data_final.rds")
write_dta(data_final, "data/data_dta/data_final.dta")
```


#Nightlight

##Round 5 (2012)

###adm1

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2012.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r5_adm1 <- data.frame()



for (country in cty_adm1) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm1 (nightlight raster)
    night_adm1 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm1 <- night_adm1
    
    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, night_adm1) %>%
      mutate(round = 5)

    night_r5_adm1 <- rbind(night_r5_adm1, regions)
}

night_r5_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r5_adm1))

saveRDS(night_r5_adm1, file="data/data_rds/night_r5_adm1.rds")
```

###adm2

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2012.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r5_adm2 <- data.frame()



for (country in cty_adm2) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm2 (nightlight raster)
    night_adm2 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm2 <- night_adm2
    
    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, night_adm2) %>%
      mutate(round = 5)

    night_r5_adm2 <- rbind(night_r5_adm2, regions)
}

night_r5_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r5_adm2))

saveRDS(night_r5_adm2, file="data/data_rds/night_r5_adm2.rds")
```

###adm3

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2012.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r5_adm3 <- data.frame()



for (country in cty_adm3) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm3 (nightlight raster)
    night_adm3 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm3 <- night_adm3
    
    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, night_adm3) %>%
      mutate(round = 5)

    night_r5_adm3 <- rbind(night_r5_adm3, regions)
}

night_r5_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r5_adm3))

saveRDS(night_r5_adm3, file="data/data_rds/night_r5_adm3.rds")
```

###adm_merge

```{r}
night_r5_adm1 <- readRDS("data/data_rds/night_r5_adm1.rds")
night_r5_adm2 <- readRDS("data/data_rds/night_r5_adm2.rds")
night_r5_adm3 <- readRDS("data/data_rds/night_r5_adm3.rds")

night_r5 <- merge(night_r5_adm1, night_r5_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
night_r5 <- merge(night_r5, night_r5_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(night_r5, file="data/data_rds/night_r5.rds")
```

##Round 6 (2015)

###adm1

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2015.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r6_adm1 <- data.frame()



for (country in cty_adm1) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm1 (nightlight raster)
    night_adm1 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm1 <- night_adm1
    
    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, night_adm1) %>%
      mutate(round = 6)

    night_r6_adm1 <- rbind(night_r6_adm1, regions)
}

night_r6_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r6_adm1))

saveRDS(night_r6_adm1, file="data/data_rds/night_r6_adm1.rds")
```

###adm2

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2015.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r6_adm2 <- data.frame()



for (country in cty_adm2) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm2 (nightlight raster)
    night_adm2 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm2 <- night_adm2
    
    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, night_adm2) %>%
      mutate(round = 6)

    night_r6_adm2 <- rbind(night_r6_adm2, regions)
}

night_r6_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r6_adm2))

saveRDS(night_r6_adm2, file="data/data_rds/night_r6_adm2.rds")
```

###adm3

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2015.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r6_adm3 <- data.frame()



for (country in cty_adm3) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm3 (nightlight raster)
    night_adm3 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm3 <- night_adm3
    
    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, night_adm3) %>%
      mutate(round = 6)

    night_r6_adm3 <- rbind(night_r6_adm3, regions)
}

night_r6_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r6_adm3))

saveRDS(night_r6_adm3, file="data/data_rds/night_r6_adm3.rds")
```

###adm_merge

```{r}
night_r6_adm1 <- readRDS("data/data_rds/night_r6_adm1.rds")
night_r6_adm2 <- readRDS("data/data_rds/night_r6_adm2.rds")
night_r6_adm3 <- readRDS("data/data_rds/night_r6_adm3.rds")

night_r6 <- merge(night_r6_adm1, night_r6_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
night_r6 <- merge(night_r6, night_r6_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(night_r6, file="data/data_rds/night_r6.rds")
```

##Round 7 (2017)

###adm1

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2017.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r7_adm1 <- data.frame()



for (country in cty_adm1) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm1 (nightlight raster)
    night_adm1 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm1 <- night_adm1
    
    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, night_adm1) %>%
      mutate(round = 7)

    night_r7_adm1 <- rbind(night_r7_adm1, regions)
}

night_r7_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r7_adm1))

saveRDS(night_r7_adm1, file="data/data_rds/night_r7_adm1.rds")
```

###adm2

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2017.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r7_adm2 <- data.frame()



for (country in cty_adm2) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm2 (nightlight raster)
    night_adm2 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm2 <- night_adm2
    
    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, night_adm2) %>%
      mutate(round = 7)

    night_r7_adm2 <- rbind(night_r7_adm2, regions)
}

night_r7_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r7_adm2))

saveRDS(night_r7_adm2, file="data/data_rds/night_r7_adm2.rds")
```

###adm3

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2017.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r7_adm3 <- data.frame()



for (country in cty_adm3) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm3 (nightlight raster)
    night_adm3 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm3 <- night_adm3
    
    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, night_adm3) %>%
      mutate(round = 7)

    night_r7_adm3 <- rbind(night_r7_adm3, regions)
}

night_r7_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r7_adm3))

saveRDS(night_r7_adm3, file="data/data_rds/night_r7_adm3.rds")
```

###adm_merge

```{r}
night_r7_adm1 <- readRDS("data/data_rds/night_r7_adm1.rds")
night_r7_adm2 <- readRDS("data/data_rds/night_r7_adm2.rds")
night_r7_adm3 <- readRDS("data/data_rds/night_r7_adm3.rds")

night_r7 <- merge(night_r7_adm1, night_r7_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
night_r7 <- merge(night_r7, night_r7_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(night_r7, file="data/data_rds/night_r7.rds")
```
##Round 8 (2020)

###adm1

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2020.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r8_adm1 <- data.frame()



for (country in cty_adm1) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm1 (nightlight raster)
    night_adm1 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm1 <- night_adm1
    
    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, night_adm1) %>%
      mutate(round = 8)

    night_r8_adm1 <- rbind(night_r8_adm1, regions)
}

night_r8_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r8_adm1))

saveRDS(night_r8_adm1, file="data/data_rds/night_r8_adm1.rds")
```

###adm2

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2020.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r8_adm2 <- data.frame()



for (country in cty_adm2) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm2 (nightlight raster)
    night_adm2 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm2 <- night_adm2
    
    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, night_adm2) %>%
      mutate(round = 8)

    night_r8_adm2 <- rbind(night_r8_adm2, regions)
}

night_r8_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r8_adm2))

saveRDS(night_r8_adm2, file="data/data_rds/night_r8_adm2.rds")
```

###adm3

```{r}
tiff_file <- "data/data_raw/nighttime_recode/Harmonized_DN_NTL_2020.tif"

night_wgs84 <- raster(tiff_file)

values(night_wgs84)[values(night_wgs84) < 0] <- 0

night_r8_adm3 <- data.frame()



for (country in cty_adm3) {
    shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    regions <- st_read(shapefile)
    regions <- st_make_valid(regions)

    shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    country_shp <- readOGR(shapefile_path)

    if (!identical(crs(night_wgs84), crs(country_shp))) {
      country_shp <- spTransform(country_shp, crs(night_wgs84))
    }

    night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
    night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

#mean_adm3 (nightlight raster)
    night_adm3 <- exact_extract(night_wgs84_masked, regions, 'mean')
    regions$night_adm3 <- night_adm3
    
    regions %<>%
      as.data.frame()

    regions %<>%
      rename(iso = GID_0) %>%
      select(iso, NAME_1, NAME_2, NAME_3, night_adm3) %>%
      mutate(round = 8)

    night_r8_adm3 <- rbind(night_r8_adm3, regions)
}

night_r8_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(night_r8_adm3))

saveRDS(night_r8_adm3, file="data/data_rds/night_r8_adm3.rds")
```

###adm_merge

```{r}
night_r8_adm1 <- readRDS("data/data_rds/night_r8_adm1.rds")
night_r8_adm2 <- readRDS("data/data_rds/night_r8_adm2.rds")
night_r8_adm3 <- readRDS("data/data_rds/night_r8_adm3.rds")

night_r8 <- merge(night_r8_adm1, night_r8_adm2, by = c("iso", "NAME_1", "round"), all = TRUE)
night_r8 <- merge(night_r8, night_r8_adm3, by = c("iso", "NAME_1", "NAME_2", "round"), all = TRUE)

saveRDS(night_r8, file="data/data_rds/night_r8.rds")
```

##Nightlight stack

```{r}
night_r5 <- readRDS("data/data_rds/night_r5.rds")
night_r6 <- readRDS("data/data_rds/night_r6.rds")
night_r7 <- readRDS("data/data_rds/night_r7.rds")
night_r8 <- readRDS("data/data_rds/night_r8.rds")

night_rounds <- list(night_r5, night_r6, night_r7, night_r8)

night_stack <- bind_rows(night_rounds)

saveRDS(night_stack, file="data/data_rds/night_stack.rds")
```

##Merge nightlight

```{r}
data_final_int <- readRDS("data/data_rds/data_final_nlp.rds")
night_stack <- readRDS("data/data_rds/night_stack.rds")

data_final_int%<>%
  select(-c("night_adm1", "night_adm2", "night_adm3"))

data_final_int_n<- data_final_int %>%
  left_join(night_stack, by = c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))

saveRDS(data_final_int_n, file="data/data_rds/data_final_int_n.rds")
```


#Lightning strikes

```{r}
ncpath <- "data/data_raw/"
ncname <- "VHRFC"  
ncfname <- paste(ncpath, ncname, ".nc", sep="")
ncin <- nc_open(ncfname)
print(ncin)

FRD <- ncvar_get(ncin, "VHRFC_LIS_FRD")
dim(FRD)

lon <- ncvar_get(ncin, "Longitude")
lat <- ncvar_get(ncin, "Latitude")

r_FRD <- raster(t(FRD), 
                xmn=min(lon), xmx=max(lon), 
                ymn=min(lat), ymx=max(lat),
                crs=CRS("+proj=longlat +datum=WGS84"))

r_FRD <- flip(r_FRD, direction = "y")

nc_close(ncin)
```

##adm1

```{r}
lis_r_adm1 <- data.frame()

for (country in cty_adm1) {

shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(r_FRD), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(r_FRD))
}

cropped <- crop(r_FRD, extent(country_shp))
masked <- mask(cropped, country_shp)

    data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
    
    
    pop_resampled <- resample(pop_wgs84, r_FRD, method="bilinear")

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    pop_resampled <- resample(pop_wgs84_masked, masked, method="bilinear")

    if (!all(res(masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

    lis_pop <- masked * pop_wgs84_resampled
    
    lis_pop_adm1 <- exact_extract(lis_pop, regions, 'mean')
    regions$lis_pop_adm1 <- lis_pop_adm1

    lis_adm1 <- exact_extract(masked, regions, 'mean')
    regions$lis_adm1 <- lis_adm1
    
    pop_adm1 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm1 <- pop_adm1
    
    regions$lis_adm1_pot <- ifelse(pop_adm1 == 0 | is.na(pop_adm1), NA, lis_pop_adm1 / pop_adm1)
  
regions %<>%
  as.data.frame()

regions %<>%
  rename(iso=GID_0)%>%
  select(iso, NAME_1, lis_adm1, lis_pop_adm1, lis_adm1_pot)

lis_r_adm1 <- rbind(lis_r_adm1, regions)
}

lis_r_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(lis_r_adm1))

saveRDS(lis_r_adm1, file="data/data_rds/lis_r_adm1.rds")
```

##adm2

```{r}
lis_r_adm2 <- data.frame()

for (country in cty_adm2) {

shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(r_FRD), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(r_FRD))
}

cropped <- crop(r_FRD, extent(country_shp))
masked <- mask(cropped, country_shp)

data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
        pop_resampled <- resample(pop_wgs84, r_FRD, method="bilinear")

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    pop_resampled <- resample(pop_wgs84_masked, masked, method="bilinear")

    if (!all(res(masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

    lis_pop <- masked * pop_wgs84_resampled
    
    lis_pop_adm2 <- exact_extract(lis_pop, regions, 'mean')
    regions$lis_pop_adm2 <- lis_pop_adm2

    lis_adm2 <- exact_extract(masked, regions, 'mean')
    regions$lis_adm2 <- lis_adm2
    
    pop_adm2 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm2 <- pop_adm2
    
    regions$lis_adm2_pot <- ifelse(pop_adm2 == 0 | is.na(pop_adm2), NA, lis_pop_adm2 / pop_adm2)
    
regions %<>%
  as.data.frame()

regions %<>%
  rename(iso=GID_0)%>%
  select(iso, NAME_1, NAME_2, lis_adm2, lis_pop_adm2, lis_adm2_pot)

lis_r_adm2 <- rbind(lis_r_adm2, regions)
}

lis_r_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(lis_r_adm2))

saveRDS(lis_r_adm2, file="data/data_rds/lis_r_adm2.rds")
```

##adm3

```{r}
lis_r_adm3 <- data.frame()

for (country in cty_adm3) {

shapefile_path <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")

country_shp <- readOGR(shapefile_path)

if (!identical(crs(r_FRD), crs(country_shp))) {
  country_shp <- spTransform(country_shp, crs(r_FRD))
}

cropped <- crop(r_FRD, extent(country_shp))
masked <- mask(cropped, country_shp)

data_file <- paste0("data/data_raw/pop_density/", country, "_pd_2012_1km_UNadj.tif")
    pop <- raster(data_file)
    pop_wgs84 <- projectRaster(pop, crs = CRS("+proj=longlat +datum=WGS84"))
        pop_resampled <- resample(pop_wgs84, r_FRD, method="bilinear")

    pop_wgs84_cropped <- crop(pop_wgs84, extent(country_shp))
    pop_wgs84_masked <- mask(pop_wgs84_cropped, country_shp)

    pop_resampled <- resample(pop_wgs84_masked, masked, method="bilinear")

    if (!all(res(masked) == res(pop_wgs84_masked))) {
      pop_wgs84_resampled <- resample(pop_wgs84_masked, masked, method = "bilinear")
    } else {
      pop_wgs84_resampled <- pop_wgs84_masked
    }

    if (!compareRaster(masked, pop_wgs84_resampled)) {
      stop("error raster matching")
    }

  shapefile <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

    lis_pop <- masked * pop_wgs84_resampled
    
    lis_pop_adm3 <- exact_extract(lis_pop, regions, 'mean')
    regions$lis_pop_adm3 <- lis_pop_adm3

    lis_adm3 <- exact_extract(masked, regions, 'mean')
    regions$lis_adm3 <- lis_adm3
    
    pop_adm3 <- exact_extract(pop_wgs84_resampled, regions, 'mean')
    regions$pop_adm3 <- pop_adm3
    
    regions$lis_adm3_pot <- ifelse(pop_adm3 == 0 | is.na(pop_adm3), NA, lis_pop_adm3 / pop_adm3)
  
regions %<>%
  as.data.frame()

regions %<>%
  rename(iso=GID_0)%>%
  select(iso, NAME_1, NAME_2, NAME_3, lis_adm3, lis_pop_adm3, lis_adm3_pot)

lis_r_adm3 <- rbind(lis_r_adm3, regions)
}

lis_r_adm3 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(lis_r_adm3))

saveRDS(lis_r_adm3, file="data/data_rds/lis_r_adm3.rds")
```

##Lightning stack

```{r}
lis_r_adm1 <- readRDS("data/data_rds/lis_r_adm1.rds")
lis_r_adm2 <- readRDS("data/data_rds/lis_r_adm2.rds")
lis_r_adm3 <- readRDS("data/data_rds/lis_r_adm3.rds")

lis_r <- merge(lis_r_adm1, lis_r_adm2, by = c("iso", "NAME_1"), all = TRUE)
lis_r <- merge(lis_r, lis_r_adm3, by = c("iso", "NAME_1", "NAME_2"), all = TRUE)

saveRDS(lis_r, file="data/data_rds/lis_r.rds")
```

##Merge lightning

```{r}
data_final_int_n <- readRDS("data/data_rds/data_final_int_n.rds")

data_final_int_n%<>%
  select(-c("lis_adm1", "lis_pop_adm1", "lis_adm1_pot","lis_adm2","lis_pop_adm2","lis_adm2_pot", "lis_adm3", "lis_pop_adm3", "lis_adm3_pot", "tv"))

lis_r <- readRDS("data/data_rds/lis_r.rds")

rounds <- data.frame(round = rep(5:8, each = nrow(lis_r)))

expanded_data <- lis_r[rep(1:nrow(lis_r), times = 4), ]

expanded_data$round <- rounds$round

expanded_data <- expanded_data %>% distinct(iso, NAME_1, NAME_2, NAME_3, round, .keep_all = TRUE)

data_final_int_n_l <- left_join(data_final_int_n, expanded_data, by=c("iso", "NAME_1", "NAME_2", "NAME_3", "round"))

data_final_int_n_l%<>%
  mutate(tv=case_when(
    round==5 ~ 1,
    round==6 ~ 2,
    round==7 ~ 3,
    round==8 ~ 4,
  ))

glimpse(data_final_int_n_l)

saveRDS(data_final_int_n_l, file="data/data_rds/data_final_int_n_l.rds")
```

#Region area

```{r}
data_final_nlp <- readRDS("data/data_rds/data_final_int_n_l.rds")

countries <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "GHA", "KEN", "MOZ", "MWI", "NGA", "TZA", "UGA", "ZMB", "ZWE")

data_keep <- subset(data_final_nlp, select = c("id_unique", "latitude", "longitude")) %>%
  filter(!is.na(latitude) & !is.na(longitude))

data_keep_sf <- st_as_sf(data_keep, coords = c("longitude", "latitude"), crs = 4326)

remove(data_keep)

all_regions_0 <- list()

for (country in countries) {
  shapefile_0 <- paste0("data/data_raw/gadm/gadm41_", country, "_0.shp")
    if (file.exists(shapefile_0)) {
      regions_0 <- st_read(shapefile_0, quiet = TRUE) %>%
        st_make_valid()
      if (is.na(st_crs(regions_0))) {
        regions_0 <- st_set_crs(regions_0, 4326)
      }
      regions_0$iso <- country
      regions_0$area_0_km2 <- as.numeric(st_area(regions_0)) / 10^6
      all_regions_0[[country]] <- regions_0
}}

df_regions_0 <- do.call(rbind, all_regions_0) %>%
  st_make_valid() %>%
  st_transform(crs = st_crs(data_keep_sf))

data_keep_sf_0 <- st_join(data_keep_sf, df_regions_0 %>% select(iso, area_0_km2), join = st_intersects)

data_keep_sf_0 %<>%
  filter(!is.na(iso) | !is.na(area_0_km2))

#adm1

all_regions_1 <- list()

for (country in countries) {
  shapefile_1 <- paste0("data/data_raw/gadm/gadm41_", country, "_1.shp")
    if (file.exists(shapefile_1)) {
      regions_1 <- st_read(shapefile_1, quiet = TRUE) %>%
        st_make_valid()
      if (is.na(st_crs(regions_1))) {
        regions_1 <- st_set_crs(regions_1, 4326)
      }
      regions_1$iso <- country
      regions_1$area_1_km2 <- as.numeric(st_area(regions_1)) / 10^6
      all_regions_1[[country]] <- regions_1
    }}

df_regions_1 <- do.call(rbind, all_regions_1) %>%
  st_make_valid() %>%
  st_transform(crs = st_crs(data_keep_sf))

data_keep_sf_1 <- st_join(data_keep_sf_0, df_regions_1 %>% select(iso, NAME_1, area_1_km2), join = st_intersects)

data_keep_sf_1 %<>%
rename(iso = iso.x) %>%
  select(-iso.y)

#adm2

all_regions_2 <- list()

for (country in countries) {
  shapefile_2 <- paste0("data/data_raw/gadm/gadm41_", country, "_2.shp")
    if (file.exists(shapefile_2)) {
      regions_2 <- st_read(shapefile_2, quiet = TRUE) %>%
        st_make_valid()
      if (is.na(st_crs(regions_2))) {
        regions_2 <- st_set_crs(regions_2, 4326)
      }
      regions_2$iso <- country
      regions_2$area_2_km2 <- as.numeric(st_area(regions_2)) / 10^6
      all_regions_2[[country]] <- regions_2
    }}

df_regions_2 <- do.call(rbind, all_regions_2) %>%
  st_make_valid() %>%
  st_transform(crs = st_crs(data_keep_sf))

data_keep_sf_2 <- st_join(data_keep_sf_1, df_regions_2 %>% select(iso, NAME_1, NAME_2, area_2_km2), join = st_intersects)

data_keep_sf_2 %<>%
rename(iso = iso.x,
       NAME_1=NAME_1.x) %>%
  select(-c("iso.y", "NAME_1.y"))


#adm3

countries_adm3 <-  countries[countries %in%cty_adm3]

all_regions_3 <- list()

for (country in countries_adm3) {
  shapefile_3 <- paste0("data/data_raw/gadm/gadm41_", country, "_3.shp")
    if (file.exists(shapefile_3)) {
      regions_3 <- st_read(shapefile_3, quiet = TRUE) %>%
        st_make_valid()
      if (is.na(st_crs(regions_3))) {
        regions_3 <- st_set_crs(regions_3, 4326)
      }
      regions_3$iso <- country
      regions_3$area_3_km2 <- as.numeric(st_area(regions_3)) / 10^6
      all_regions_3[[country]] <- regions_3
    }}

df_regions_3 <- do.call(rbind, all_regions_3) %>%
  st_make_valid() %>%
  st_transform(crs = st_crs(data_keep_sf))

data_keep_sf_3 <- st_join(data_keep_sf_2, df_regions_3 %>% select(iso, NAME_1, NAME_2, NAME_3, area_3_km2), join = st_intersects)

data_keep_sf_3 %<>%
rename(iso = iso.x,
       NAME_1=NAME_1.x,
       NAME_2 = NAME_2.x) %>%
  select(-c("iso.y", "NAME_1.y", "NAME_2.y"))

data_area_region <- as.data.frame(data_keep_sf_3)%>%select(-c("geometry", "id_unique"))

saveRDS(data_area_region, file="data/data_rds/data_area_region.rds")


data_final_nlp2%<>%
  select(-c( "area_0_km2", "area_1_km2", "area_2_km2", "area_3_km2"))

data_final_nlp2 %<>% left_join(data_area_region, by=c("iso", "NAME_1", "NAME_2", "NAME_3"))%>%
  distinct(id_unique, .keep_all = TRUE)

saveRDS(data_final_nlp2, file="data/data_rds/data_final_nlp2.rds")
```

#Various variable creation

```{r}
data_final_nlp2 <- readRDS("data/data_rds/data_final.rds")

#remove too long variables for stata
data_final_nlp2%<>%
  select(-c(dist_cap_ncap_quint_mean_norm_all, dist_cap_sndncap_quint_max_norm_all, dist_cap_sndncap_quint_mean_norm_all, dist_cap_sndncap_dec_max_norm_all, dist_cap_sndncap_dec_mean_norm_all))

#region variables
countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")

data_final_nlp2%<>%
  select(-c("lis_region", "pop_region", "night_region", "lis_region_pot", "lis_region_log", "pop_region_log", "night_region_log"))

data_final_nlp2 %<>%
mutate(lis_region = case_when(
    iso %in% countries_adm1 ~ lis_adm1,
    iso %in% countries_adm2 ~ lis_adm2, 
    TRUE ~ NA_integer_
  ))%>%
mutate(pop_region = case_when(
    iso %in% countries_adm1 ~ pop_adm1,
    iso %in% countries_adm2 ~ pop_adm2, 
    TRUE ~ NA_integer_
  ))%>%
  mutate(night_region = case_when(
    iso %in% countries_adm1 ~ night_adm1,
    iso %in% countries_adm2 ~ night_adm2, 
    TRUE ~ NA_integer_
  ))%>%
  mutate(lis_region_log=log(lis_region+1))%>%
  mutate(pop_region_log=log(pop_region+1))%>%
  mutate(night_region_log=log(night_region+1))

data_final_nlp2%<>%
  mutate(lis_region_pot = case_when(
    iso %in% countries_adm1 ~ lis_adm1_pot,
    iso %in% countries_adm2 ~ lis_adm2_pot, 
    TRUE ~ NA_integer_
  ))


##add president birthplace (region)
data_president <- read_xlsx("data/data_raw/data_president.xlsx")
data_president%<>%
  filter(!is.na(date_of_election))

unique_combinations <- data_president %>%
  distinct(iso, round)

#countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

results <- data.frame()

for (i in 1:nrow(unique_combinations)) {
  
  iso <- unique_combinations$iso[i]
  round <- unique_combinations$round[i]
  
  data_filtered <- data_president %>%
    filter(iso == !!iso, round == !!round)
  
  if (nrow(data_filtered) == 0) {
    warning(paste("Pas de données pour le pays", iso, "et la période", round))
    next
  }
  
  shapefile_path <- paste0("data/data_raw/gadm/gadm41_", iso, "_1.shp")
  
  if (file.exists(shapefile_path)) {
    regions_sf <- st_read(shapefile_path)
    regions_sf <- st_make_valid(regions_sf)
    
    presidents_sf <- st_as_sf(data_filtered, coords = c("long_nais", "lat_nais"), crs = 4326)
    
    presidents_with_region <- st_join(presidents_sf, regions_sf, join = st_within)
    
    presidents_with_region$iso <- iso
    presidents_with_region$round <- round
    
    results <- rbind(results, presidents_with_region)
    
  } else {
    warning(paste("Shapefile pour le pays", iso, "n'existe pas dans le chemin spécifié."))
  }
}

results%<>%
  select(iso, round, NAME_1)

results%<>%
  select(-geometry)

results%<>%
  rename(NAME_1_pres=NAME_1)


data_final_nlp2%<>%
  select(-c("pres_adm1", "pres_adm2"))

data_final_nlp2 %<>% left_join(results, by=c("iso", "round"))

data_final_nlp2 %<>%
  mutate(pres_adm1=ifelse(NAME_1_pres==NAME_1, 1, 0))

data_final_nlp2%<>%
  select(-geometry)


#individual variables
data_final_nlp2 %<>%
mutate(age = na_if(age, -1) %>% na_if(998) %>% na_if(999))%>%
mutate(age_2=age*age)%>%
mutate(educ_sec=case_when(
    educ %in% c(5, 6,7,8,9) ~ 1,
    educ %in% c(0,1,2, 3, 4) ~0,
    TRUE ~ NA_integer_))%>%
mutate(conditions_country = if_else(conditions_country %in% c(1, 2, 3, 4, 5), conditions_country, NA_integer_))%>%
mutate(bin_conditions_country=ifelse(conditions_country>=3, 1, 0))%>%
mutate(conditions_eco = if_else(conditions_eco %in% c(1, 2, 3, 4, 5), conditions_eco, NA_integer_))%>%
mutate(bin_conditions_eco = if_else(is.na(conditions_eco), NA_integer_, if_else(conditions_eco >= 3, 1L, 0L)))%>%
mutate(emp = if_else(emp %in% c(0, 1, 2, 3), emp, NA_integer_))%>%
mutate(bin_emp = case_when(emp %in% c(0, 1) ~ 0,
                           emp %in% c(2, 3) ~ 1,
                           TRUE ~ NA_integer_))%>%
mutate(tele_news = if_else(tele_news %in% c(0, 1, 2, 3, 4), tele_news, NA_integer_))%>%
mutate(paper_news = if_else(paper_news %in% c(0, 1, 2, 3, 4), paper_news, NA_integer_))%>%
mutate(radio_news = if_else(radio_news %in% c(0, 1, 2, 3, 4), radio_news, NA_integer_))%>%
mutate(internet_news = if_else(internet_news %in% c(0, 1, 2, 3, 4), internet_news, NA_integer_))%>%
mutate(sm_news = if_else(sm_news %in% c(0, 1, 2, 3, 4), sm_news, NA_integer_))%>%
mutate(internet_use = if_else(internet_use %in% c(0, 1, 2, 3, 4), internet_use, NA_integer_))%>%
mutate(feelnat = if_else(feelnat %in% c(1, 2, 3, 4, 5), feelnat, NA_integer_))%>%
mutate(trust_parl_a = if_else(trust_parl %in% c(0, 1, 2, 3), trust_parl, NA_integer_))%>%
mutate(trust_pres_a = if_else(trust_pres %in% c(0, 1, 2, 3), trust_pres, NA_integer_))%>%
mutate(trust_elec_a = if_else(trust_elec %in% c(0, 1, 2, 3), trust_elec, NA_integer_))%>%
mutate(unfair_eth = if_else(conditions_eco %in% c(0, 1, 2, 3), unfair_eth, NA_integer_))%>%
mutate(bin_unfair_eth = case_when(unfair_eth %in% c(0, 1) ~ 0,
                           unfair_eth %in% c(2, 3) ~ 1,
                           TRUE ~ NA_integer_))%>%
mutate(unfair_eth = as.numeric(unfair_eth)) %>%
 mutate(bin_unfair_eth = case_when(
    unfair_eth == 0 ~ 0,  # Never -> 0
    unfair_eth == 1 ~ 0,  # Sometimes -> 0
    unfair_eth == 2 ~ 1,  # Often -> 1
    unfair_eth == 3 ~ 1,  # Always -> 1
    TRUE ~ NA_real_       # All other cases -> NA
  )) %>%
  mutate(disc_pol_a=if_else(disc_pol %in% c(0, 1, 2), disc_pol, NA_integer_))

data_final_nlp2 %<>%
 group_by(id_unique)%>%
  mutate(pol_trust = ifelse(all(is.na(c(trust_pres_a, trust_parl_a))), NA, weighted.mean(c(trust_pres_a, trust_parl_a), na.rm = TRUE)))%>%
  ungroup()


#cluster variables
data_final_nlp2 %<>%
mutate(country_round=as.numeric(paste0(round,ccode)))

cty_sample <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

data_final_nlp2%<>%
  mutate(spl=if_else(iso%in%cty_sample, 1, 0))
```

#Country variables

```{r}
##correction: add colonial origin
data_color <- read_xlsx("data/data_raw/color.xlsx") 

data_final_nlp2 %<>% left_join(data_color, by="iso")
rm(data_color)

juriglobe <- read_excel("data/data_raw/FR_index.xlsx")

juriglobe %<>%
  rename(gov_type = "Forme\r\nde gouvernement") %>%
  mutate(
    gov_type = case_when(
      gov_type == "Présidentiel" ~ "presidential",
      gov_type == "Parlementaire" ~ "parliamentarian",
      gov_type == "Semi-présidentiel" ~ "semi_presidential",
      gov_type == "Monarchique" ~ "monarchical",
      TRUE ~ NA_character_
    ),
    presidential = as.numeric(gov_type == "presidential"),
    parlementarian = as.numeric(gov_type == "parliamentarian"),
    semi_presidential = as.numeric(gov_type == "semi_presidential"),
    monarchical = as.numeric(gov_type == "monarchical")
  ) %>%
  select(iso, presidential, parlementarian, semi_presidential, monarchical, gov_type)

data_final_nlp2 %<>% left_join(juriglobe, by="iso")

rm(juriglobe)

data_final_nlp2%<>%
  select(-geometry)

gdppc <- read_excel("data/data_raw/gdppc.xls")%>%
  rename(iso=ISO)%>%
  select(iso, gdpcap_2012, gdpcap_2015, gdpcap_2017, gdpcap_2020)
pop <- read_excel("data/data_raw/pop.xls")%>%
  rename(iso=ISO)%>%
  select(iso, pop_2012, pop_2015, pop_2017, pop_2020)
area <- read_excel("data/data_raw/area.xls")%>%
  select(iso, area_2012, area_2015, area_2017, area_2020)
cor_index <- read_excel("data/data_raw/cor_index.xlsx")%>%
  rename(iso=ISO)%>%
  select(iso, cor_2012, cor_2015, cor_2017, cor_2020)

data_cty <- list(
  cor_index,
  gdppc,
  pop,
  area
)

var_cty <- reduce(data_cty, inner_join, by = "iso")

var_cty %<>%
  mutate(across(-iso, as.numeric))

glimpse(var_cty)

data_final_nlp2%<>%
  select(-c("gdppc", "gdppc_log", "cor_index", "area", "area_log", "pop"))

data_final_nlp2 %<>% left_join(var_cty, by = "iso")

data_final_nlp2 %<>%
mutate(cor_index = case_when(
    round == 5 ~ cor_2012,
    round == 6 ~ cor_2015,
    round == 7 ~ cor_2017,
    round == 8 ~ cor_2020,
    TRUE ~ NA
  ))

data_final_nlp2 %<>%
mutate(gdppc = case_when(
    round == 5 ~ gdpcap_2012,
    round == 6 ~ gdpcap_2015,
    round == 7 ~ gdpcap_2017,
    round == 8 ~ gdpcap_2020,
    TRUE ~ NA
  ))

data_final_nlp2 %<>%
mutate(pop = case_when(
    round == 5 ~ pop_2012,
    round == 6 ~ pop_2015,
    round == 7 ~ pop_2017,
    round == 8 ~ pop_2020,
    TRUE ~ NA
  ))

data_final_nlp2 %<>%
mutate(area = case_when(
    round == 5 ~ area_2012,
    round == 6 ~ area_2015,
    round == 7 ~ area_2017,
    round == 8 ~ area_2020,
    TRUE ~ NA
  ))

data_final_nlp2%<>%
  select(-c(cor_2012, cor_2015, cor_2017, cor_2020, gdpcap_2012, gdpcap_2015, gdpcap_2017, gdpcap_2020, pop_2012, pop_2015, pop_2017, pop_2020, area_2012, area_2015, area_2017, area_2020))

data_final_nlp2%<>%
  mutate(gdppc_log=log(gdppc+1))%>%
  mutate(area_log=log(area+1))


qog <- read.csv("data/data_raw/qog_std_ts_jan24.csv")

countries <- unique(data_final_nlp2$iso)

qog%<>%
  filter(ccodealp %in% countries)

qog%<>%
  select(year, ccodealp, aii_q55, aii_q56, fhp_mcpp5, vdem_mecorrpt, vdem_polyarchy)%>%
  rename(iso=ccodealp, fh_med_index=fhp_mcpp5, med_self_censor=aii_q55, citiz_self_censor=aii_q56, vdem_med_corrupt=vdem_mecorrpt)


qog%<>%
  rename(round=year)%>%
  mutate(round=case_when(round==2012 ~ 5,
                   round==2015 ~ 6,
                   round==2017 ~ 7,
                   round==2020 ~ 8))

data_final_nlp2%<>%
  select(-c( "med_self_censor", "citiz_self_censor", "fh_med_index", "vdem_med_corrupt", "vdem_polyarchy"))

data_final_nlp2 %<>% left_join(qog, by=c("iso", "round"))

data_final_nlp2%<>%
  mutate(color_num = as.numeric(factor(color)))

data_final_nlp2%<>%
  mutate(gov_num = as.numeric(factor(gov_type)))
```

#Individual variables

```{r}
#Correction sex
afro_stack <- readRDS("data/data_rds/afro_stack.rds")

data_final_nlp2%<>%select(-sex)

afro_stack %<>%
  mutate(sex = as.numeric(sex)) %>%
  mutate(sex = case_when(
    sex == 1 ~ 0,  # Male -> 0
    sex == 2 ~ 1,  # Female -> 1
    TRUE ~ NA_integer_
  ))%>%
  select(id_unique, sex)

data_final_nlp2%<>%
  left_join(afro_stack, by="id_unique")

#Correction rural

data_final_nlp2%<>%select(-c("rural", "bin_rural"))

afro_stack <- readRDS("data/data_rds/afro_stack.rds")

afro_stack %<>%
  mutate(bin_rural = case_when(
    round == 5 & rural == 1 ~ 0,  # Urban in round 5 -> 0
    round == 5 & rural == 2 ~ 1,  # Rural in round 5 -> 1
    round == 6 & rural == 1 ~ 0,  # Urban in round 6 -> 0
    round == 6 & rural == 2 ~ 1,  # Rural in round 6 -> 1
    round == 7 & rural %in% c(1, 3, 460) ~ 0,  # Urban, Semi-Urban, Peri-Urban
    round== 7 & rural == 2 ~ 1, # Rural in round 7 -> 1
    round == 8 & rural %in% c(1, 3) ~ 0,  # Urban, Semi-Urban, Peri-Urban in round 8 -> 0
    round == 8 & rural == 2 ~ 1,  # Rural in round 8 -> 1
    TRUE ~ NA_integer_  # NA for all other cases
  ))

afro_stack%<>%
  select(id_unique, rural, bin_rural)

data_final_nlp2%<>%
  left_join(afro_stack, by="id_unique")
```

```{r}
#vote_oppo

afro_w5 <- read.csv("data/data_raw/afrobarometer/afb_full_r5.csv_")
afro_w6 <- read.csv("data/data_raw/afrobarometer/afb_full_r6.csv_")
afro_w7 <- read_sav("data/data_raw/afrobarometer/R7_Merged data_34ctry_4Dec18.sav")
afro_w8 <- read_sav("data/data_raw/afrobarometer/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

data_final_nlp2%<>%
  select(-c("vote_party", "vote_oppo"))

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q99)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q99)%>%
  rename(vote_party=Q99)

data_final_nlp2 <- left_join(data_final_nlp2, afro_w8, by="id_unique")


rm(afro_w8)


afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))


afro_w7%<>%
  select(RESPNO, Q99)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q99)%>%
  rename(vote_party=Q99)


data_final_nlp2 <- left_join(data_final_nlp2, afro_w7, by="id_unique")


data_final_nlp2%<>%
  mutate(vote_party = case_when(
    round == 7 ~ vote_party.y,
    round == 8 ~ vote_party.x))

data_final_nlp2%<>%
  select(-c(vote_party.y, vote_party.x))

rm(afro_w7)


afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q99)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q99)%>%
  rename(vote_party=q99)


data_final_nlp2 <- left_join(data_final_nlp2, afro_w6, by="id_unique")


data_final_nlp2%<>%
  mutate(vote_party = case_when(
    round == 6 ~ vote_party.y,
    round %in% c(7,8) ~ vote_party.x))

data_final_nlp2%<>%
  select(-c(vote_party.y, vote_party.x))


rm(afro_w6)


afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q99)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q99)%>%
  rename(vote_party=q99)


data_final_nlp2 <- left_join(data_final_nlp2, afro_w5, by="id_unique")

data_final_nlp2%<>%
  mutate(vote_party = case_when(
    round == 5 ~ vote_party.y,
    round %in% c(6,7,8) ~ vote_party.x))

data_final_nlp2%<>%
  select(-c(vote_party.y, vote_party.x))


rm(afro_w5)

data_final_nlp2%<>%
mutate(vote_party = case_when(
  vote_party %in% c(9995, 9997, 9998, 9999, -1) ~ NA_real_,
  TRUE ~ vote_party
))


data_final_nlp2%<>%
  select(-c("year_of_election", "date_of_election", "winner"))


data_elections_R <- na.omit(read_excel("data/data_raw/data_elections_R.xlsx", 
    col_types = c("text", "numeric", "numeric", 
        "date", "numeric")))

data_final_nlp2 %<>% left_join(data_elections_R, by=c("iso","round"))

data_final_nlp2$vote_party <- as.numeric(zap_labels(data_final_nlp2$vote_party))

data_final_nlp2$vote_oppo <- ifelse(data_final_nlp2$winner!=data_final_nlp2$vote_party, 1,0)
```

```{r}
#growth_country

data_final_nlp2 <- readRDS("data/data_rds/data_final.rds")

afro_w5 <- read.csv("data/data_raw/afrobarometer/afb_full_r5.csv_")
afro_w6 <- read.csv("data/data_raw/afrobarometer/afb_full_r6.csv_")
afro_w7 <- read_sav("data/data_raw/afrobarometer/R7_Merged data_34ctry_4Dec18.sav")
afro_w8 <- read_sav("data/data_raw/afrobarometer/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q6A)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q6A)%>%
  rename(growth_country=Q6A)

data_final_nlp2 <- left_join(data_final_nlp2, afro_w8, by="id_unique")


rm(afro_w8)


afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))


afro_w7%<>%
  select(RESPNO, Q6)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q6)%>%
  rename(growth_country=Q6)


data_final_nlp2 <- left_join(data_final_nlp2, afro_w7, by="id_unique")


data_final_nlp2%<>%
  mutate(growth_country = case_when(
    round == 7 ~ growth_country.y,
    round == 8 ~ growth_country.x))

data_final_nlp2%<>%
  select(-c(growth_country.y, growth_country.x))

rm(afro_w7)


afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q6)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q6)%>%
  rename(growth_country=q6)


data_final_nlp2 <- left_join(data_final_nlp2, afro_w6, by="id_unique")


data_final_nlp2%<>%
  mutate(growth_country = case_when(
    round == 6 ~ growth_country.y,
    round %in% c(7,8) ~ growth_country.x))

data_final_nlp2%<>%
  select(-c(growth_country.y, growth_country.x))


rm(afro_w6)


afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q5a)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q5a)%>%
  rename(growth_country=q5a)


data_final_nlp2 <- left_join(data_final_nlp2, afro_w5, by="id_unique")

data_final_nlp2%<>%
  mutate(growth_country = case_when(
    round == 5 ~ growth_country.y,
    round %in% c(6,7,8) ~ growth_country.x))

data_final_nlp2%<>%
  select(-c(growth_country.y, growth_country.x))


rm(afro_w5)

data_final_nlp2%<>%
mutate(growth_country = if_else(growth_country %in% c(1, 2, 3, 4, 5), growth_country, NA_integer_))

data_final_nlp2 %<>%
  mutate(across(
    .cols = c(perf_corr, perf_crime, perf_eco, perf_educ, perf_elect, perf_health, 
              perf_ineq, perf_job, perf_local, perf_parl, perf_pres, perf_price, 
              perf_road, perf_water, perf_trad),
    .fns = ~ if_else(. %in% c(1, 2, 3, 4), ., NA_integer_)
  ))  

data_final_nlp2%<>%
   group_by(id_unique)%>%
  mutate(perf_mean=mean(c(perf_eco, perf_job, perf_poor, perf_price, perf_ineq, perf_crime, perf_health, perf_educ, perf_water, perf_corr, perf_road, perf_elect), na.rm = TRUE))%>%
  ungroup()

data_final_nlp2%<>%
mutate(corr_level = if_else(corr_level %in% c(1, 2, 3, 4, 5), corr_level, NA_integer_))

data_final_nlp2%<>%
mutate(corr_parl_a = if_else(corr_parl %in% c(0, 1, 2, 3), corr_parl, NA_integer_))%>%
mutate(corr_pres_a = if_else(corr_pres %in% c(0, 1, 2, 3), corr_pres, NA_integer_))%>%
mutate(corr_local_a = if_else(corr_local %in% c(0, 1, 2, 3), corr_local, NA_integer_))%>%
mutate(corr_trad_a = if_else(corr_trad %in% c(0, 1, 2, 3), corr_trad, NA_integer_))%>%
mutate(corr_judge_a = if_else(corr_judge %in% c(0, 1, 2, 3), corr_judge, NA_integer_))

data_final_nlp2%<>%
  group_by(id_unique)%>%
  mutate(pol_corr = ifelse(all(is.na(c(corr_pres_a, corr_parl_a))), NA, weighted.mean(c(corr_pres_a, corr_parl_a), na.rm = TRUE)))%>%
  ungroup()
```

```{r}
#perf_poor

data_final_nlp2 <- readRDS("data/data_rds/data_final.rds")

afro_w5 <- read.csv("data/data_raw/afrobarometer/afb_full_r5.csv_")
afro_w6 <- read.csv("data/data_raw/afrobarometer/afb_full_r6.csv_")
afro_w7 <- read_sav("data/data_raw/afrobarometer/R7_Merged data_34ctry_4Dec18.sav")
afro_w8 <- read_sav("data/data_raw/afrobarometer/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q50B)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q50B)%>%
  rename(perf_poor=Q50B)

data_final_nlp2 <- left_join(data_final_nlp2, afro_w8, by="id_unique")


rm(afro_w8)


afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))


afro_w7%<>%
  select(RESPNO, Q56B)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q56B)%>%
  rename(perf_poor=Q56B)


data_final_nlp2 <- left_join(data_final_nlp2, afro_w7, by="id_unique")


data_final_nlp2%<>%
  mutate(perf_poor = case_when(
    round == 7 ~ perf_poor.y,
    round == 8 ~ perf_poor.x))

data_final_nlp2%<>%
  select(-c(perf_poor.y, perf_poor.x))

rm(afro_w7)


afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q66b)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q66b)%>%
  rename(perf_poor=q66b)


data_final_nlp2 <- left_join(data_final_nlp2, afro_w6, by="id_unique")


data_final_nlp2%<>%
  mutate(perf_poor = case_when(
    round == 6 ~ perf_poor.y,
    round %in% c(7,8) ~ perf_poor.x))

data_final_nlp2%<>%
  select(-c(perf_poor.y, perf_poor.x))


rm(afro_w6)


afro_w5%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w5%<>%
  select(respno, q65b)%>%
  rename(id=respno)

afro_w5%<>%
  mutate(round=5)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q65b)%>%
  rename(perf_poor=q65b)


data_final_nlp2 <- left_join(data_final_nlp2, afro_w5, by="id_unique")

data_final_nlp2%<>%
  mutate(perf_poor = case_when(
    round == 5 ~ perf_poor.y,
    round %in% c(6,7,8) ~ perf_poor.x))

data_final_nlp2%<>%
  select(-c(perf_poor.y, perf_poor.x))


rm(afro_w5)

data_final_nlp2%<>%
mutate(perf_poor = if_else(perf_poor %in% c(1, 2, 3, 4), perf_poor, NA_integer_))
```

```{r}
data_final_nlp2%<>%
  mutate(bin_feelnat = case_when(
      !is.na(feelnat) & feelnat %in% c(4, 5) ~ 1,
      !is.na(feelnat) & feelnat %in% c(1, 2, 3) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp2%<>%
  mutate(check_citiz_a = if_else(check_citiz %in% c(1, 2, 3, 4, 5), check_citiz, NA_integer_))%>%
  mutate(check_parl_a = if_else(check_parl %in% c(1, 2, 3, 4, 5), check_citiz, NA_integer_))


data_final_nlp2 %<>%
  mutate(bin_check_citiz = case_when(
    !is.na(check_citiz_a) & check_citiz_a %in% c(1, 2, 5) ~ 0,
    !is.na(check_citiz_a) & check_citiz_a %in% c(3, 4) ~ 1,
    TRUE ~ NA_integer_
  ))

data_final_nlp2 %<>%
  mutate(bin_check_parl = case_when(
    !is.na(check_parl_a) & check_parl_a %in% c(1, 2, 5) ~ 0,
    !is.na(check_parl_a) & check_parl_a %in% c(3, 4) ~ 1,
    TRUE ~ NA_integer_
  ))


data_final_nlp2%<>%
  mutate(assoc_a = if_else(assoc %in% c(0, 1, 2, 3), assoc, NA_integer_))%>%
  mutate(commu_a = if_else(commu %in% c(0, 1, 2, 3, 4), commu, NA_integer_))%>%
  mutate(prob_a = if_else(prob %in% c(0, 1, 2, 3, 4), prob, NA_integer_))

data_final_nlp2%<>%
  mutate(elec_fair_a = if_else(elec_fair %in% c(1, 2, 3, 4), elec_fair, NA_integer_))%>%
  mutate(pref_demo_a = if_else(pref_demo %in% c(1, 2, 3), pref_demo, NA_integer_))%>%
  mutate(protest_a = if_else(protest %in% c(0, 1, 2, 3, 4), protest, NA_integer_))%>%
  mutate(vote_a = if_else(vote %in% c(0, 1, 2, 3, 4, 5 ,6 , 7), vote , NA_integer_))%>%
  mutate(bin_vote = case_when(
    !is.na(vote_a) & vote_a %in% c(0, 2, 3, 4, 5 ,6 , 7) ~ 0,
    !is.na(vote_a) & vote_a == 1 ~ 1,
    TRUE ~ NA_integer_
  ))

data_final_nlp2 <- readRDS("data/data_rds/data_final_r.rds")

data_final_nlp2%<>%
  mutate(trust_gen_a=if_else(trust_gen%in%c(0,1), trust_gen, NA_integer_))

data_final_nlp2%<>%
  mutate(extent_a = if_else(extent %in% c(1, 2, 3, 4), extent, NA_integer_))%>%
  mutate(satis_demo_a = if_else(satis_demo %in% c(0, 1, 2, 3, 4), satis_demo, NA_integer_))

data_final_nlp2%<>%
  mutate(bin_corr_parl_a = case_when(
      !is.na(corr_parl_a) & corr_parl_a %in% c(2, 3) ~ 1,
      !is.na(corr_parl_a) & corr_parl_a %in% c(0, 1) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp2%<>%
  mutate(bin_corr_pres_a = case_when(
      !is.na(corr_pres_a) & corr_pres_a %in% c(2, 3) ~ 1,
      !is.na(corr_pres_a) & corr_pres_a %in% c(0, 1) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp2%<>%
  mutate(bin_trust_parl_a = case_when(
      !is.na(trust_parl_a) & trust_parl_a %in% c(2, 3) ~ 1,
      !is.na(trust_parl_a) & trust_parl_a %in% c(0, 1) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp2%<>%
  mutate(bin_trust_pres_a = case_when(
      !is.na(trust_pres_a) & trust_pres_a %in% c(2, 3) ~ 1,
      !is.na(trust_pres_a) & trust_pres_a %in% c(0, 1) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp2 %<>%
 group_by(id_unique)%>%
  mutate(bin_pol_trust = ifelse(all(is.na(c(bin_trust_pres_a, bin_trust_parl_a))), NA_integer_, weighted.mean(c(bin_trust_pres_a, bin_trust_parl_a), na.rm = TRUE)))%>%
  ungroup()

data_final_nlp2 %<>%
 group_by(id_unique)%>%
  mutate(bin_pol_corr = ifelse(all(is.na(c(bin_corr_pres_a, bin_corr_parl_a))), NA_integer_, weighted.mean(c(bin_corr_pres_a, bin_corr_parl_a), na.rm = TRUE)))%>%
  ungroup()


data_final_nlp2%<>%
  mutate(bin_pol_trust_2 = case_when(
      !is.na(bin_pol_trust) & bin_pol_trust %in% c(0.5, 1) ~ 1,
      !is.na(bin_pol_trust) & bin_pol_trust == 0 ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp2%<>%
  mutate(bin_pol_corr_2 = case_when(
      !is.na(bin_pol_corr) & bin_pol_corr %in% c(0.5, 1) ~ 1,
      !is.na(bin_pol_corr) & bin_pol_corr == 0 ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp2%<>%
  group_by(latitude, longitude)%>%
  mutate(ea_id = cur_group_id()) %>%
  mutate(ea_round=as.numeric(paste0(ea_id,round)))%>%
  ungroup()

data_final_nlp2%<>%
  mutate(region = case_when(
    iso %in%c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE") ~ name2_id, 
    iso %in% c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE") ~ name1_id,
    TRUE ~ NA_integer_
  ))

data_final_nlp2%<>%
  mutate(bin_growth_country = case_when(
      !is.na(growth_country) & growth_country %in% c(3, 4, 5) ~ 1,
      !is.na(growth_country) & growth_country %in% c(1,2) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp2%<>%
  mutate(bin_internet_news = case_when(
      !is.na(internet_news) & internet_news %in% c(3, 4, 5) ~ 1,
      !is.na(internet_news) & internet_news %in% c(0, 1,2) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp2%<>%
  mutate(bin_paper_news = case_when(
      !is.na(paper_news) & paper_news %in% c(3, 4, 5) ~ 1,
      !is.na(paper_news) & paper_news %in% c(0, 1,2) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp2%<>%
  mutate(bin_radio_news = case_when(
      !is.na(radio_news) & radio_news %in% c(3, 4, 5) ~ 1,
      !is.na(radio_news) & radio_news %in% c(0, 1,2) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp2%<>%
  mutate(bin_tele_news = case_when(
      !is.na(tele_news) & tele_news %in% c(3, 4, 5) ~ 1,
      !is.na(tele_news) & tele_news %in% c(0, 1,2) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp2%<>%
  mutate(bin_sm_news = case_when(
      !is.na(sm_news) & sm_news %in% c(3, 4, 5) ~ 1,
      !is.na(sm_news) & sm_news %in% c(0, 1,2) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp2%<>%
  mutate(bin_internet_use = case_when(
      !is.na(internet_use) & internet_use %in% c(3, 4, 5) ~ 1,
      !is.na(internet_use) & internet_use %in% c(0, 1,2) ~ 0,
      TRUE ~ NA_integer_))

data_final_nlp2%<>%
  mutate(bin_disc_pol_a = case_when(
      !is.na(disc_pol_a) & disc_pol_a %in% c(1, 2) ~ 1,
      !is.na(disc_pol_a) & disc_pol_a == 0 ~ 0,
      TRUE ~ NA_integer_))

```

```{r}
data_final_nlp2 <- readRDS("data/data_rds/data_final_r.rds")

afro_w5 <- read.csv("data/data_raw/afrobarometer/afb_full_r5.csv_")
afro_w6 <- read.csv("data/data_raw/afrobarometer/afb_full_r6.csv_")
afro_w7 <- read_sav("data/data_raw/afrobarometer/R7_Merged data_34ctry_4Dec18.sav")
afro_w8 <- read_sav("data/data_raw/afrobarometer/R8.Merge_34ctry_2nov21.release.w.local.info.sav")

afro_w8%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))

afro_w8%<>%
  select(RESPNO, Q86B)%>%
  rename(id=RESPNO)

afro_w8%<>%
  mutate(round=8)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q86B)%>%
  rename(neig_eth=Q86B)

data_final_nlp2 <- left_join(data_final_nlp2, afro_w8, by="id_unique")


rm(afro_w8)


afro_w7%<>%
  filter(!is.na(EA_GPS_LA))%>%
  filter(!is.na(LOCATION.LEVEL.2))%>%
  filter(!duplicated(RESPNO))


afro_w7%<>%
  select(RESPNO, Q87B)%>%
  rename(id=RESPNO)

afro_w7%<>%
  mutate(round=7)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, Q87B)%>%
  rename(neig_eth=Q87B)


data_final_nlp2 <- left_join(data_final_nlp2, afro_w7, by="id_unique")


data_final_nlp2%<>%
  mutate(neig_eth = case_when(
    round == 7 ~ neig_eth.y,
    round == 8 ~ neig_eth.x))

data_final_nlp2%<>%
  select(-c(neig_eth.y, neig_eth.x))

rm(afro_w7)


afro_w6%<>%
  filter(!is.na(latitude))%>%
  filter(!is.na(locationlevel2))%>%
  filter(!duplicated(respno))

afro_w6%<>%
  select(respno, q89b)%>%
  rename(id=respno)

afro_w6%<>%
  mutate(round=6)%>%
  mutate(id_unique=paste0(id,round))%>%
  select(id_unique, q89b)%>%
  rename(neig_eth=q89b)


data_final_nlp2 <- left_join(data_final_nlp2, afro_w6, by="id_unique")


data_final_nlp2%<>%
  mutate(neig_eth = case_when(
    round == 6 ~ neig_eth.y,
    round %in% c(7,8) ~ neig_eth.x))

data_final_nlp2%<>%
  select(-c(neig_eth.y, neig_eth.x))


rm(afro_w6)

data_final_nlp2%<>%
  mutate(neig_eth_a = if_else(neig_eth %in% c(1, 2, 3, 4, 5), neig_eth, NA_integer_))
```

```{r}
data_final_nlp2%<>%
  mutate(dist_cap_10=dist_cap/10,
         dist_ncap_10=dist_ncap/10,
         dist_sndncap_10=dist_sndncap/10,
         dist_cap_max_norm_2=dist_cap_max_norm*dist_cap_max_norm,
         dist_cap_max_norm_3=dist_cap_max_norm*dist_cap_max_norm*dist_cap_max_norm,
         dist_ncap_max_norm_2=dist_ncap_max_norm*dist_ncap_max_norm,
         dist_ncap_max_norm_3=dist_ncap_max_norm*dist_ncap_max_norm*dist_ncap_max_norm,
         dist_sndncap_max_norm_2=dist_sndncap_max_norm*dist_sndncap_max_norm,
         dist_sndncap_max_norm_3=dist_sndncap_max_norm*dist_sndncap_max_norm*dist_sndncap_max_norm
         )
```


```{r}
data_final_nlp2 <- readRDS("data/data_rds/data_final_r.rds")

data_final_nlp2%<>%
  group_by(NAME_2, round)%>%
  mutate(internet_news_adm2=mean(internet_news),
         sm_news_adm2=mean(sm_news),
         internet_use_adm2=mean(internet_use))

```


```{r}
table(data_final_nlp2$neig_eth_a)
hist(data_final_nlp2$neig_eth_a)
```

#Export Stata

```{r}
saveRDS(data_final_nlp2, file="data/data_rds/data_final_r.rds")

write_dta(data_final_nlp2, "data/data_dta/data_final_r.dta")
```

```{r}
#Media freedom and democracy indexes

data_final <- readRDS("data/data_rds/data_final.rds")

qog <- read.csv("data/data_raw/qog_std_ts_jan24.csv")

countries <- data_final %>% filter(spl == 1) %>% pull(iso) %>% unique()

qog %<>%
  select(year, ccodealp, rsf_pfi1321, ) %>%
  rename(iso = ccodealp, rsf_index = rsf_pfi1321)

qog %<>%
  mutate(round = case_when(
    year == 2013 ~ 5,
    between(year, 2014, 2015) ~ 6,
    between(year, 2016, 2018) ~ 7,
    between(year, 2019, 2021) ~ 8,
    TRUE ~ NA_integer_
  ))

qog %<>%
  group_by(iso, round) %>%
  mutate(rsf_index_mean = ifelse(is.na(rsf_index), NA_integer_, mean(rsf_index, na.rm = TRUE))) %>%
  ungroup()

qog %<>%
  filter(!is.na(round)) %>%
  distinct(iso, round, .keep_all = TRUE) %>%
  filter(iso %in% countries) %>%
  mutate(rsf_index_med_all = ifelse(is.na(round), NA_integer_, median(rsf_index_mean, na.rm =
                                                                        TRUE)))
qog %<>%
  select(iso,
         round,
         rsf_index_mean)

data_final %<>% left_join(qog, by = c("iso", "round"))

saveRDS(data_final, file = "data/data_rds/data_final.rds")

write_dta(data_final, "data/data_dta/data_final.dta")

vdem <- readRDS("data/data_raw/V-Dem-CY-Full+Others-v13.rds")

vdem %<>%
  select(country_text_id, year, v2x_polyarchy, e_polity2)

vdem %<>%
  filter(country_text_id %in% countries)

vdem %<>%
  rename(iso = country_text_id) %>%
  mutate(round = case_when(
    between(year, 2011, 2013) ~ 5,
    between(year, 2014, 2015) ~ 6,
    between(year, 2016, 2018) ~ 7,
    between(year, 2019, 2021) ~ 8,
    TRUE ~ NA_integer_
  ))

vdem %<>%
  group_by(iso, round) %>%
  filter(!is.na(round)) %>%
  mutate(
    v2x_polyarchy_mean2 = ifelse(all(is.na(v2x_polyarchy)), NA_integer_, mean(v2x_polyarchy, na.rm = TRUE)),
    e_polity2_mean2 = ifelse(all(is.na(e_polity2)), NA_integer_, mean(e_polity2, na.rm = TRUE))
  ) %>%
  ungroup()

vdem %<>%
  select(iso, round, v2x_polyarchy_mean2, e_polity2_mean2) %>%
  distinct(iso, round, .keep_all = TRUE)

data_final %<>% left_join(vdem, by = c("iso", "round"))

saveRDS(data_final, file = "data/data_rds/data_final.rds")

write_dta(data_final, "data/data_dta/data_final.dta")

```